Pillar 1 - Sequential Pattern Mining

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
Expanded transcripts

### Transactions for Apriori
```{r making transactions}

@@

```
#Experiments
#Visualizing rules
```{r}
#look at counts
ggplot(for_plots, aes(LHS))+
  geom_bar()

#jitter
ggplot(manual_confidence_rules)+
  geom_jitter(mapping=aes(x=Conf_corr, y=log(support), color=lift_corr))

ggplot(manual_confidence_rules)+
  geom_jitter(mapping=aes(x=log(support), y=lift_corr, color = Conf_corr))

#heatmap
ggplot(select(manual_confidence_rules,LHS,RHS, n_rule), aes(x=RHS,y=LHS, fill=n_rule))+
  geom_raster() +
  theme(
    axis.text.x = element_text(angle=90)
  )

gglot(table(select(manual_confidence_rules,LHS,RHS)))

#ggnetwork

#SEE: http://kateto.net/network-visualization 
g_net <- graph_from_data_frame(d=head(for_plots,50), directed=T) #I BELIEVE THE COLUMNS SHOULD BE REVERSED.

l <- layout_in_circle(g_net)
plot(g_net, #vertex.shape="none",
     vertex.size=.9,
     #vertex.label=NA,
     vertex.label.cex=0.5,
     edge.arrow.size=.1, 
     edge.curved=.1,
     layout=l)

```
#Visualisation
It might be a nice idea to visualise using Sankey diagrams, although I don't know if there will be too many courses for it to be meaningful. We might need to sample. See https://analyzecore.com/2014/10/31/sequence-carts-analysis-sankey/

#EXPERIMENTS:

##TO MOVE UP (These are ready:)
Rounds grades and add new row from original grade up to 10.
NOTE: includes mandatory courses.
```{r}

distributed_transcript <- d_transcript %>%
  filter(!is.na(Grade), Grade>=0) %>%
  mutate(Round_grade = paste("g", round(Grade,0),sep=""),
         Values = T) %>%
  spread(key = "Round_grade", value = Values) %>%
  mutate(g1  = g0|g1,
         g2  = g1|g2,
         g3  = g2|g3,
         g4  = g3|g4,
         g5  = g4|g5,
         g6  = g5|g6,
         g7  = g6|g7,
         g8  = g7|g8,
         g9  = g8|g9,
         g10 = g9|g10
         ) %>%
  gather(key="Gr_string", value="Gr_bool", g0, g1, g2, g3, g4,g5,g6,g7,g8,g9,g10, na.rm=T) %>%
  select(-Gr_bool )%>%
  separate(Gr_string, into=c("Trash", "Grade_new"), sep="g")%>%
  select(-Trash) %>%
  mutate(Grade= as.numeric(Grade_new))%>%
  select(-Grade_new) #%>%
  #to check that the grades appear from original grade to 10.
  #arrange(`Student ID`, `Course ID`)

@@

>>>>

```
###Expanded Transcripts
```{r}

d_transcript_expanded <- d_transcript %>%
  filter(!is.na(Grade), Grade>=0) %>%
  mutate(Round_grade = paste("g", round(Grade,0),sep=""),
         Values = T) %>%
  spread(key = "Round_grade", value = Values) %>%
  mutate(g1  = g0|g1,
         g2  = g1|g2,
         g3  = g2|g3,
         g4  = g3|g4,
         g5  = g4|g5,
         g6  = g5|g6,
         g7  = g6|g7,
         g8  = g7|g8,
         g9  = g8|g9,
         g10 = g9|g10
         ) %>%
  gather(key="Gr_string", value="Gr_bool", g0, g1, g2, g3, g4,g5,g6,g7,g8,g9,g10, na.rm=T) %>%
  select(-Gr_bool )%>%
  separate(Gr_string, into=c("Trash", "Grade_new"), sep="g")%>%
  select(-Trash) %>%
  mutate(Grade= as.numeric(Grade_new))%>%
  select(-Grade_new) #%>%
  #to check that the grades appear from original grade to 10.
  #arrange(`Student ID`, `Course ID`)

#changing to transactions

d_transactions_expanded <- d_course %>%

  # Join with transcripts.
  select(- Period) %>%
  inner_join(d_transcript_expanded, by = "Course ID") %>%

    item_PF = paste(`Course ID`, PF, sep = "_"),
    item_HL = paste(`Course ID`, HL, sep = "_")
    ) %>%
  rename(
    item = `Course ID`
  ) 
#%>%
  #arrange(sequenceID, item) %>%
  #select(sequenceID, item, Grade, everything())
```
### Transactions for Apriori
```{r making transactions}

@@

@@

#EXPERIMENTS:
##TO MOVE UP (These are ready:)
Rounds grades and add new row from original grade up to 10.
NOTE: includes mandatory courses.
